### 2017-06-20 Doc/classicthesis/Chapters/Conclusions.tex
ieee
tercer borrador

Finally, we are very thankful to IBM's grant for the \textit{Privacy Preserving Identity Management applied to IoT} project, which allowed us to get this far. Also, this paper will be presented for publication in a JCR magazine.

@@

	Our sixth objective, that we couldn't get to design in depth. The original idea was to integrate in a FIWARE\footnote{FIWARE \url{https://www.fiware.org/}} environment the Fiware Keyrock and Idemix Issuer, so both, users and IoT devices' identities are managed in the IdM\footnote{Identity Management - KeyRock \url{https://catalogue.fiware.org/enablers/identity-management-keyrock}} system. The Issuer generates credentials based on the user’s attributes held in the Keyrock, and IoT devices can authenticate against Fi-ware services (using Idemix), or authenticate against other IoT devices (M2M).

>>>>

Finally, we are very thankful to IBM's grant for the \textit{Privacy Preserving Identity Management applied to IoT} project, which allowed us to get this far. Also, in \autoref{ch:JCR} we show the version for publication in a JCR magazine.

@@

	Our sixth objective, that we couldn't get to design in depth. The original idea was to integrate in a FIWARE\footnote{FIWARE \url{https://www.fiware.org/}} environment the Fiware Keyrock and Idemix Issuer, so both users and IoT's identities are managed in the IdM\footnote{Identity Management - KeyRock \url{https://catalogue.fiware.org/enablers/identity-management-keyrock}} system. The Issuer generates credentials based on the user’s attributes held in the Keyrock, and IoT devices can authenticate against Fi-ware services (using Idemix), or authenticate against other IoT devices (M2M).

### 2017-06-20 Doc/classicthesis/Chapters/Introduccion.tex
ieee
tercer borrador

@@

El objetivo de este proyecto es integrar Idemix con el Internet de las Cosas. Para ello nos apoyaremos en el proyecto europeo de ABC4Trust, \ac{P2ABCE}\footnote{P2ABCEngine \url{https://github.com/p2abcengine/p2abcengine}}, que define una arquitectura común, lenguaje y artefactos para unificar distintas soluciones como Idemix de IBM, o U-Prove de Microsoft. Con esto todo dispositivo IoT que lo implemente será compatible con el ecosistema existente.

>>>>

In traditional M2M (Machine to Machine) environments the issues about security and privacy have already been treated deeply, but in the IoT world, due to it's recent and fast growth, lacks of those tools to solve autonomously these problems.

En entornos tradicionales, los problemas de seguridad y privacidad ya han sido tratados en profundidad, pero en el mundo de IoT, debido a su reciente y rápido crecimiento, carece de esas herramientas para resolver estos problemas.

@@

Como parte de la beca académica de IBM para \textit{Administración de Identidad Preservando la Privacidad aplicada a Internet de las Cosas}, el objetivo de este proyecto es integrar Idemix con el Internet de las Cosas. Para ello nos apoyaremos en el proyecto europeo de ABC4Trust, \ac{P2ABCE}\footnote{P2ABCEngine \url{https://github.com/p2abcengine/p2abcengine}}, que define una arquitectura común, lenguaje y artefactos para unificar distintas soluciones como Idemix de IBM, o U-Prove de Microsoft. Con esto todo dispositivo IoT que lo implemente será compatible con el ecosistema existente.
